---
title: "1. R Basics Exercise"
author: "Junho Lee"
date: "1/11/2019"
output: html_document
---
##### What is two to the power of five?
```{r}
2^5
```

##### Create a vector called stock.prices with the following data points: 23,27,23,21,34
```{r}
stock.prices <- c(23,27,23,21,34)
```

##### Assign names to the price data points relating to the day of the week, starting with Mon, Tue, Wed, etc...
```{r}
names(stock.prices) = c('Mon','Tues','Wed','Thu','Fri')
```

##### What was the average (mean) stock price for the week? (You may need to reference a built-in function)
```{r}
mean(stock.prices)
```

##### Create a vector called over.23 consisting of logicals that correspond to the days where the stock price was more than $23
```{r}
over23 <- stock.prices > 23
```

##### Use the over.23 vector to filter out the stock.prices vector and only return the day and prices where the price was over $23
```{r}
stock.prices[over23]
```

##### Use a built-in function to find the day the price was the highest
```{r}
stock.prices[stock.prices == max(stock.prices)]
```