---
title: "2. R Matrix Exercises"
author: "Junho Lee"
date: "1/11/2019"
output: html_document
---
##### Ex 1: Create 2 vectors A and B, where A is (1,2,3) and B is (4,5,6). With these vectors, use the cbind() or rbind() function to create a 2 by 3 matrix from the vectors. You'll need to figure out which of these binding functions is the correct choice.

```{r}
a <- c(1,2,3)
b <- c(4,5,6)
my.data <- rbind(a,b)
```

##### Ex 2: Create a 3 by 3 matrix consisting of the numbers 1-9. Create this matrix using the shortcut 1:9 and by specifying the nrow argument in the matrix() function call. Assign this matrix to the variable mat

```{r}
mat <- matrix(1:9, nrow=3)
```
##### Ex 3: Confirm that mat is a matrix using is.matrix()

```{r}
is.matrix(mat)
```

##### Ex 4: Create a 5 by 5 matrix consisting of the numbers 1-25 and assign it to the variable mat2. The top row should be the numbers 1-5.

```{r}
mat2 <-matrix(1:25, byrow=T, nrow=5)
```

##### Ex 5: Using indexing notation, grab a sub-section of mat2 from the previous exercise that looks like this:

```{r}
mat2[2:3,2:3]
```

##### Ex 6: Using indexing notation, grab a sub-section of mat2 from the previous exercise that looks like this:
```{r}
mat2[4:5,4:5]
```

##### Ex 7: What is the sum of all the elements in mat2?

```{r}
sum(mat2)
```

##### Ex 8: Ok time for our last exercise! Find out how to use runif() to create a 4 by 5 matrix consisting of 20 random numbers (4*5=20).

```{r}
ran.matrix <- matrix(runif(20, min = 0, max = 100), nrow=4)
print(ran.matrix)
```