---
title: "3. R Data Frames Exercises"
author: "Junho Lee"
date: "1/12/2019"
output: html_document
---
Ex 1: Recreate the following dataframe by creating vectors and using the data.frame function:

```{r}
age <- c(22,25,26)
weight <- c(150,165,120)
sex <- c('M','M','F')

name <- c('Sam','Frank','Amy')


my.data.frame <- data.frame(row.names = name,age,weight,sex)
my.data.frame
```

Ex 2: Check if mtcars is a dataframe using is.data.frame()
```{r}
is.data.frame(mtcars)
```

Ex 3: Use as.data.frame() to convert a matrix into a dataframe:
```{r}
mat <- matrix(1:25,nrow = 5)
as.data.frame(mat)
```

Ex 4: Set the built-in data frame mtcars as a variable df. We'll use this df variable for the rest of the exercises.
```{r}
df <- mtcars
```

Ex 5: Display the first 6 rows of df
```{r}
head(df,6)
```

Ex 6: What is the average mpg value for all the cars?
```{r}
mean(df$mpg)
```

Ex 7: Select the rows where all cars have 6 cylinders (cyl column)
```{r}
df[df$cyl==6,]

subset(df,cyl==6)
```

Ex 8: Select the columns am,gear, and carb.
```{r}
df[,c('am','gear','carb')]
```

Ex 9: Create a new column called performance, which is calculated by hp/wt.
```{r}
df$performance <- df$hp/df$wt
head(df)
```

Ex 10: Your performance column will have several decimal place precision. Figure out how to use round() (check help(round)) to reduce this accuracy to only 2 decimal places.
```{r}
df$performance <- round(df$hp/df$wt,2)
head(df)
```

Ex 11: What is the average mpg for cars that have more than 100 hp AND a wt value of more than 2.5.
```{r}
mean(df[df$hp>100 & df$wt > 2.5,]$mpg)
mean(subset(df, hp>100 & wt > 2.5)$mpg)
```

Ex 11: What is the mpg of the Hornet Sportabout?
```{r}
df['Hornet Sportabout',]$mpg
```