---
title: "4. Conditional Statements Exercises"
author: "Junho Lee"
date: "1/12/2019"
output: html_document
---

Exercise Problems

Ex 1: Write a script that will print "Even Number" if the variable x is an even number, otherwise print "Not Even":
```{r}
x <- 12

if (x%%2 == 0) {
  print('Even Number')
} else {
  print('Not Even')
}
```

Ex 2: Write a script that will print 'Is a Matrix' if the variable x is a matrix, otherwise print "Not a Matrix". Hint: You may want to check out help(is.matrix)
```{r}
x <- matrix()

if (is.matrix(x)) {
  print('Is a Matrix')
} else {
  print('Not a Matrix')
}
```

Ex 3: Create a script that given a numeric vector x with a length 3, will print out the elements in order from high to low. You must use if,else if, and else statements for your logic. (This code will be relatively long)
```{r}
x <- c(3,7,1)

if ((x[1] > x[2]) & (x[1] > x[3])) {
  if (x[2] > x[3]) {
    print(paste(x[1], x[2], x[3]))
  } else {
    print(paste(x[1], x[3], x[2]))    
  }
} else if  ((x[2] > x[1]) & (x[2] > x[3])) {
  if (x[1]>x[3]) {
        print(paste(x[2], x[1], x[3]))
  } else {
        print(paste(x[2], x[3], x[1]))
  }
} else {
  if (x[1]>x[2]) {
    print(paste(x[3], x[1], x[2]))
  } else {
    print(paste(x[3], x[2], x[1]))
  }
}
```

Ex 4: Write a script that uses if,else if, and else statements to print the max element in a numeric vector with 3 elements.
```{r}
x <- c(20, 10, 1)

if ((x[1] > x[2]) & (x[1] > x[3])) {
  print(x[1])
} else if ((x[2] > x[1]) & (x[2] > x[3])) {
  print(x[2])
} else {
  print(x[3])
}
```