---
title: "7. ggplot2 Exercises"
author: "Junho Lee"
date: "1/13/2019"
output: html_document
---
Important Note!
Some of the images may be distorted from the conversion to a web format

For the first few plots, use the mpg dataset
```{r}
library(ggplot2)
library(ggthemes)
head(mpg)
```

Histogram of hwy mpg values:
```{r}
pl <- ggplot(mpg,aes(x=hwy))
print(pl + geom_histogram(bins=20, fill='red',alpha=0.5))
```

Barplot of car counts per manufacturer with color fill defined by cyl count
```{r}
pl <- ggplot(mpg,aes(x=manufacturer))
pl2 <- pl + geom_bar(aes(fill=factor(cyl)))
print(pl2)
```

Switch now to use the txhousing dataset that comes with ggplot2
```{r}
head(txhousing)
```

Create a scatterplot of volume versus sales. Afterwards play around with alpha and color arguments to clarify information.
```{r}
pl <- ggplot(txhousing,aes(x=sales, y=volume))
pl2 <- pl + geom_point(alpha=0.5, size=1, color='blue')
print(pl2)
```

Add a smooth fit line to the scatterplot from above. Hint: You may need to look up geom_smooth()
```{r}
pl3 <- pl + geom_point(alpha=0.5, size=1, color='blue') + geom_smooth(colour='red')
print(pl3)
```