---
title: "1.1 Linear Regression"
output: html_document
---


## 1.1 Linear Regression - Practice


```{r}
# Read CSV, use the delimiter (sep) to separate each field
df <- read.csv('student-mat.csv',sep = ';')
head(df)
```

Get the summary of the data
```{r}
summary(df)
```

### Clean the Data
Check if any data is missing
```{r}
any(is.na(df))
```
Now that we confirmed the dataset has no NA or NULL values.

Look at the data to observe the structure and make sure that categorical variables have a factor set to them.
```{r}
str(df)
```

## Exploratory Data Analysis
Let's use ggplot2 to explroe the data.
```{r}
library(ggplot2)
library(ggthemes)
library(dplyr)
```

Now, let's look at correlation and plot a CorrPlot to explore data, and observe if any interaction terms. Note that we exclude categorical data and grab the numberical data only.
```{r}
# Num only
num.cols <- sapply(df,is.numeric)
# Filter
cor.data <- cor(df[,num.cols])
print(cor.data) 
```

```{r}
# Load library
library(corrgram)
library(corrplot)
```

```{r}
print(corrplot(cor.data, method = 'color'))
```

```{r}
ggplot(df,aes(x=G3)) + geom_histogram(bins=20,alpha=0.5,fill='blue') + theme_minimal()
```

Split Data into Train and Test Set
```{r}
#install.packages(('caTools'))
library(caTools)

# Set A Seed
set.seed(101)

# Split up sample
sample <- sample.split(df$G3, SplitRatio = 0.7)
# 70% of data -> train
train <- subset(df, sample == TRUE)
# 30% will be test
test <- subset(df, sample == FALSE)

# Train and build model
model <- lm(G3 ~., data = train)

# Run Model

# Interpret the model
print(summary(model))
```

```{r}
# Predictions
G3.predictions <- predict(model,test)

results <- cbind(G3.predictions, test$G3)
colnames(results) <- c('predicted','actual')
results <- as.data.frame(results)
print(head(results))
```


Take care of negative score
```{r}
# Write a function
to_zero <- function(x) {
  if (x<0) {
    return(0)
  } else{
    return(x)
  }
}

# Apply the function
results$predicted <- sapply(results$predicted, to_zero)

# Mean Squared Error
mse <- mean( (results$actual - results$predicted)^2)
print(mse)

# RMSE
print(mse^0.5)
```

```{r}
SSE = sum((results$predicted - results$actual)^2)
SST = sum( (mean(df$G3) - results$actual)^2)

R2 = 1 - SSE/SST
R2


```